Data Specialization for a Staged Lambda Calculus

### 2014-11-07 paper/splitting.tex
few comments about stage one splitting

The rule for $\next$ simply tuples up the precomputation of its subexpression with a trivial immediate result,
while the rule for $\prev$ projects the combined result of its subexpression to isolate the precomputation.
It may seem like this $\prev$ rule is throwing information away, but we well show later that the first component 
of the evaluated form of $c$ in the $\prev$ rule must always be unit.
The $\pause$ rule treats the entire combined result of its subexpression as a precomputation, 
and projects out the integer result in the resumer.%
\footnote{The resumer of an integer expression is usually trivial, 
but we have to include it here for termination purposes.}

In the splitting rules for stage \bbone\ {\tt case} expressions, we
have enough information at stage \bbone\ to know what branch to take, so there's
no need to evaluate both sides. Instead, we evaluate the stage \bbone\ portion of the
taken branch only, and inject the precomputation into a sum type. In the
resumer, we case on that injection, and resume the stage \bbtwo\ portion of the
correct branch.

>>>>

In general, the

The rule for $\next$ simply tuples up the precomputation of its subterm with a trivial immediate result,
while the rule for $\prev$ projects the combined result of its subterm to isolate the precomputation.
Since the argument to $\prev$ must have a $\fut$ type, its immediate result must reduce to \texttt{()},
justifying why that part can be thrown away.
The $\pause$ rule treats the entire combined result of its subexpression as a precomputation, 
and projects out the integer result in the resumer.% 
\footnote{The resumer of an integer expression is usually trivial, 
but we have to include it here for termination purposes.}

At stage \bbone\ {\tt case}s, the splitting rules adds injections to the precomputations of each branch. 
This is then cased in the resumer to resume the stage \bbtwo\ portion of the correct branch.
This rule and $\pause$ are the only two places where nontrivial information is added to the precomputation.
